\documentclass[a4paper,12pt]{article}
\usepackage{fancyhdr}
\author{Dane Johnson}
\title{Linear Programming}
\pagestyle{fancy}
\begin{document}
\maketitle
\begin{enumerate}
\item {\it What is the worst case of the simplex algorithm? Can you prove it mathematically?} The worst case of the
  simplex algorithm in $O({{n+m}\choose{n}})$. This is because the basic and non-basic variables must be, at worst, pivoted
  into every position, thus the combinatorial aspect of the time complexity.
\item {\it What are the two main components of Linear programming?} The two main components of Linear programming are
  linear inequalities and an objective function.
\item {\it Provide a general algebraic formulation for Linear programming.} Given
  \begin{enumerate}
  \item Variables $\vec{x} = <x_{1}, x_{2}, \ldots, x_{n}>$
  \item Objective function $\vec{c}\cdot\vec{x} = c_1x_1 + c_2x_2 + \ldots + c_nx_n$
  \item Inequalities $A\vec{x} \leq \vec{b}$
  \end{enumerate}
  Maximize $\vec{c}\cdot\vec{x}$ s.t. $A\vec{x} \leq \vec{b}, \vec{x} \geq 0$
\item {\it What is meant by the duality of Linear programming?} The duality of lLnear programming means that one
  of the products of a Linear programming algorithm is a short certificate of optimization of the returned values.
\item {\it Describe the shortest path algorithm using Linear programming.} To use Linear programming to solve shortest path,
  generate all triangle inequalities to serve as the linear constraints, minimizing each of these values, and then
  selecting the maximum value from the distance vector for each end point.
\end{enumerate}

\end{document}
